supplementary figures

### 2020-05-01 PBMC.Rmd
after review

```{r Import Kenya data}
#Import the clinical enrollment data from the cleaned merged epi file
    QFT<- read.csv("/Applications/Old Computer/Epi Project/Data_clean/complete-kenya-filledin.csv")
#The studyIDs of coenrolled people are NK#_TRU# and we want just the NK# to match the lab notes
    QFT$Donor<-tstrsplit(QFT$StudyID, "_")[[1]]
#trim the data set to only those study IDs in the lab notes and select the columns you want
    QFT<-dplyr::select(QFT, Donor, age, sex, QFT, SchistosomaIntensity)%>%
        dplyr::filter(Donor %in% pbmc$Donor)
```

>>>>

```{r Import Kenya data}
#Import the clinical enrollment data from the cleaned merged epi file
    QFT<- read.csv("/Applications/Old Computer/Epi Project/Data_clean/complete-kenya-filledin.csv")
#The studyIDs of coenrolled people are NK#_TRU# and we want just the NK# to match the lab notes
    QFT$Donor<-tstrsplit(QFT$StudyID, "_")[[1]]
#trim the data set to only those study IDs in the lab notes and select the columns you want
    QFT<-dplyr::select(QFT, Donor, age, sex, QFT, HB, SchistosomaIntensity)%>%
        dplyr::filter(Donor %in% pbmc$Donor)
```

### 2020-05-01 PaperFigures.Rmd
after review

---
title: "Paper Figures"
author: "Taryn McLaughlin"
date: "8/28/2019"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, comment=NA, warning=FALSE, echo=FALSE)
library(dplyr)
library(knitr)
library(ggplot2)
library(gridExtra)
library(GGally)
library(ggpubr)
library(cowplot)
library(tidyr)
library(reshape2)
library(cowplot)
library(corrplot)
library(sjPlot)
```

>>>>

phen---
title: "Paper Figures"
author: "Taryn McLaughlin"
date: "8/28/2019"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, comment=NA, warning=FALSE, echo=FALSE)
library(dplyr)
library(knitr)
library(ggplot2)
library(gridExtra)
library(GGally)
library(ggpubr)
library(cowplot)
library(tidyr)
library(reshape2)
library(cowplot)
library(corrplot)
library(sjPlot)
```

### 2020-05-01 SuppFigures.Rmd
after review

#ICS Supplementary

>>>>

#ICS Supplementary
```{r}
pep<-plot_filter(CYT[(CYT$Stim=="PEP" & CYT$TB!="HC"),])
my_comparisons <- list(c("HC","LTBI"), 
                           c("TB", "LTBI"), 
                           c("HC", "TB"))

ggplot(pep, aes(x=TB, y=IFNg, fill=TB))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape=NA)+
    scale_fill_manual(values =c("#2166ac", "#b2182b"))+
    theme_classic()+ theme(legend.position="none")+
    theme(text = element_text(size=16)) + 
    theme(plot.subtitle = element_text(hjust = 0.5)) +
    stat_compare_means(method="wilcox.test", label.x=1.3, size=10, label="p.format")
